Holomorphic field theories and higher algebra

### 2023-08-17 highervertexops.tex
more res

Define
\beqn
\op{Res} \colon \sfA \to \C[1]
\eeqn
by the rules that $\op{Res}|_{\sfA^0} = 0$ and
\beqn
\op{Res} \left(f(z,\lambda) \omega \right) = p (f(z,\lambda)) (z=0) .
\eeqn

\begin{lem} The following are true regarding the higher algebraic residue:
\begin{enumerate}
\item The residue is $\lie{sl}(2)$ invariant.
\item For $f \in \C[z_1,z_2]$ one has $\op{Res}(f \omega) = f(0)$.
\item For any $f \in \sfA$ one has $\op{Res}(\dbar f) = 0$.
\end{enumerate}
\end{lem}
\begin{proof}
Item (1) holds since $p$ is the $\lie{sl}(2)$-equivariant projection. 
For (2), note that for $f \in \C[z_1,z_2]$ that $p(f) = f$.

@@

>>>>

Define
\beqn
\op{Res} \colon \sfA \to \C[-1]
\eeqn
by the rules that $\op{Res}|_{\sfA^0} = 0$ and
\beqn
\op{Res} \left(f(z,\lambda) \omega \right) = p (f(z,\lambda)) (z=0) .
\eeqn

\begin{lem}
\label{lem:res} 
The following are true regarding the higher algebraic residue:
\begin{enumerate}
\item The residue is $\lie{sl}(2)$ invariant.
\item For $f \in \C[z_1,z_2]$ one has $\op{Res}(f \omega) = f(0)$.
\item For any $f \in \sfA$ one has $\op{Res}(\dbar f) = 0$.
\end{enumerate}
\end{lem}
\begin{proof}
Item (1) holds since $p$ is the $\lie{sl}(2)$-equivariant projection. 
For (2), note that for $f \in \C[z_1,z_2]$ that $p(f) = f$.

@@

In the single-variable case, the residue map defines an identification
\beqn
\C((z)) \simeq \Omega^1 (\Hat{D})^\vee = \left(\C((z)) \d z\right)^\vee
\eeqn
where the right hand side is the continuous linear dual.
Explicitly, this identification takes a Laurent series $f$ to the functional 
\beqn
g \d z \mapsto \op{Res}_{1d} (f g \d z) .
\eeqn

\begin{prop}
The higher algebraic residue defines a cochain map
\beqn
\sfA \to \left(\sfA \, \d^2 z\right)^\vee [-1]
\eeqn 
which sends an element $a \in \sfA$ to the functional
\beqn
F_a \colon b \, \d^2 z \in \sfA\, \d^2 z \mapsto (-1)^{|a|} \Res(a b \, \d^2 z) .
\eeqn
\brian{weird sign, but I think it's there because of the $[-1]$ shift.}
When extended to the completed version of punctured affine space, this assignment defines an isomorphism of cochain complexes 
\beqn
F \colon \Hat\sfA \simeq \left(\Hat\sfA \, \d^2 z\right)^\vee [-1] .
\eeqn
\end{prop}
\begin{proof}
Suppose that $a \in \sfA^0$. 
Then
\begin{align*}
F_{\dbar a} (b \d^2 z) & = - \Res \left( (\dbar a) b \d^2 z \right) \\
& = - \Res\left( \dbar(a b \d^2 z) \right) + \Res \left(a \dbar b \d^2 z\right) \\
& = F_{a} (\dbar b \d^2 z) .
\end{align*}
In the final line we have used (3) from lemma \ref{lem:res}.
If $a \in \sfA^1$ then $F_{\dbar a}(b \d^2 z) = 0 = F_{a} (\dbar b \d^2 z)$ for all $b$.

\brian{Can you help me prove part 2?}
\end{proof}
